---
title: "RWorksheet_LLANERA#4b"
author: "LlaneraExerRepo"
date: "2024-12-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Using the for loop, create an R script that will display a 5x5 matrix as shown in
Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.
Hint Use abs() function to get the absolute value

2. Print the string "*" using for() function. The output should be the same as shown
in Figure
```{r}

vectorA <- c(1, 2, 3, 4, 5)


matrix <- matrix(0, nrow = 5, ncol = 5)


for (i in 1:5) {
  for (j in 1:5) {
    matrix[i, j] <- abs(i - j)
    cat(matrix[i, j], " ")
  }
  cat("\n")
}


for (i in 1:5) {
  for (j in 1:i) {
    cat("*")
  }
  cat("\n")
}

```
3. Get an input from the user to print the Fibonacci sequence starting from the 1st input up to 500. Use repeat and break statements. Write the R Scripts and its output.
```{r}

start_number <- readline(prompt = "Enter the starting number: ")


start_number <- as.numeric(start_number)


fib_1 <- 0
fib_2 <- 1


print(fib_1)


repeat {

  fib_next <- fib_1 + fib_2
  

  print(fib_next)

  fib_1 <- fib_2
  fib_2 <- fib_next


  if (fib_next > 500) {
    break
  }
}
```
```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
