---
title: "LlaneraWorksheet#3"
author: "LlaneraExerRepo"
date: "2024-10-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 1,
 A. 
```{r}
Survey <- data.frame(
  RespondentID = c(1:20),
  Gender = c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2, 2, 1,2),
  Fathers = c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1),
  HouseholdSize = c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6),
  SchoolSiblings = c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2),
  HomeType = c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2)
)

Survey
```
B
```{r}
str(Survey)
summary(Survey)
```
C.

```{r}
meanSchoolSiblings <- mean(Survey$SchoolSiblings)
meanSchoolSiblings
```
D. 

```{r}
subset_Respondents <- subset(Survey, RespondentID <= 2)
subset_Respondents
```
E. 
```{r}
specificData <- Survey[c(3,5), c("Gender", "HouseholdSize")]
specificData
```
F. 
```{r}
homeTypes <- Survey$HomeType
homeTypes
```
G.
```{r}
maleFarmers <- Survey[Survey$GEnder == 1 & Survey$Fathers == 1, ]
maleFarmers
```
H. 
```{r}
femaleManySiblings <- Survey[Survey$Gender == 2 & Survey$SchoolSiblings >= 5, ]
femaleManySiblings
```
2. 
```{r}
dataf_empty <- data.frame(
  Ints = integer(), 
  Doubles = double(), 
  Strings = character(), 
  Booleans = logical(), 
  Categories = factor(), 
  stringsAsFactors = FALSE
)
print("Structure of the empty data frame:")
str(dataf_empty)
```
3. 
A. 
```{r}
HouseHold <- read.csv("HouseholdData.csv")
HouseHold
```
B. 
```{r}
HouseHold$Sex <- factor(HouseHold$Sex, levels = c("Male", "Female"), labels = c(1, 2))
HouseHold$Sex <- as.integer(HouseHold$Sex)
HouseHold
```
C.
```{r}
HouseHold$Types.of.Houses <- factor(HouseHold$Types.of.Houses, 
                                     levels = c("Wood", "Concrete", "Semi-concrete"), 
                                     labels = c(1, 2, 3))
HouseHold$Types.of.Houses <- as.integer(HouseHold$Types.of.Houses)
HouseHold
```
D. 
```{r}
HouseHold$Fathers.Occupation <- factor(HouseHold$Fathers.Occupation, 
                                       levels = c(1, 2, 3), 
                                       labels = c("Farmer", "Driver", "Others"))
HouseHold
```
E. 
```{r}
femaleDriver <- subset(HouseHold, Sex == 2 & Fathers.Occupation == "Driver")
femaleDriver
```
```{r}
SiblingSchool <- subset(HouseHold, Siblings.at.School >= 5)
SiblingSchool
```
4. 
The graph indicates that from July 14 to July 21, 2020, the number of negative tweets surpassed that of any other type each day. Positive tweets ranked second, while neutral tweets were the least frequent.





## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
